Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-14 ieee_paper.tex
updated instruction set in conclusion.

Using a matrix with $64^3$ (or $96^3$ rows, we achieve a speedup of
xxx relative to the base case of one derivative and one function (1/1
case), relative to a potential speedup of 16. We have achieved a
speed of 100 Gflop/s on 60 cores using 240 threads, or a speed of 61\% of
maximum possible performance. The maximum possible speed for the 1/1
case is around 40 Gflop/s, of which we achieve 20 Gflop/s. On matrices
that exceed the cache, a reverse Cuthill-McKee is applied to reduce the
bandwidth, with an associated speedup of 30\% up to 135 Gflop/s. Our
optimal implementation makes use of the AVX instruction set \todo{that's not AVX on MIC, not sure what the name is}, which
makes use of swizzling and channel swapping operations for an
extremely efficient tensor product implementation. A straightforward
implementation without vectorization runs at around 35 Gflops, or 16\% of peak
performance. RCM has no effect because the number of floating point
operations is excessive (the algorithm does not fill the vector
registers to capacity).

>>>>

Using a matrix with $64^3$ (or $96^3$ rows, we achieve a speedup of
xxx relative to the base case of one derivative and one function (1/1
case), relative to a potential speedup of 16. We have achieved a
speed of 100 Gflop/s on 60 cores using 240 threads, or a speed of 61\% of
maximum possible performance. The maximum possible speed for the 1/1
case is around 40 Gflop/s, of which we achieve 20 Gflop/s. On matrices
that exceed the cache, a reverse Cuthill-McKee is applied to reduce the
bandwidth, with an associated speedup of 30\% up to 135 Gflop/s. Our
optimal implementation makes use of the (as yet unreleased) IMCI MIC instruction set 
%\todo{that's not AVX on MIC, not sure what the name is}, 
which includes a number of swizzling and channel swapping operations, for an
extremely efficient tensor product implementation. A straightforward
implementation without vectorization runs at around 35 Gflops, or 16\% of peak
performance. RCM has no effect because the number of floating point
operations is excessive (the algorithm does not fill the vector
registers to capacity).
